%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt, a4paper]{moderncv}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[margin={1cm, 1cm, 1cm, 1cm}]{geometry}
\usepackage{natbib}

\moderncvtheme[grey]{classic}

\addto\captionsenglish{\renewcommand\refname{Publications}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\firstname{Adrien}
\familyname{BOUGOUIN}
\title{\Large{\textsc{Ph.D}} \large{in Computer Science / Software Engineer}}
\address{
  Minimal Technologies,\\
  Minamiazabu Minato-ku 5-2-39 Nyu Towa Bldg 302,\\
}{
  106-0047, Tokyo, Japan
}
\homepage{http://adrien-bougouin.github.io}
\social[linkedin][https://www.linkedin.com/in/adrienbougouin]{adrien-bougouin}
\social[github][https://github.com/adrien-bougouin]{adrien-bougouin}
%\email{adrien.bougouin@univ-nantes.fr}
%\secondemail{adrien.bougouin@gmail.com}
\email{adrien.bougouin@gmail.com}
\extrainfo{
  06/06/1989\\
  Married
}

\begin{document}
  \maketitle

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %% Education
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \section{\textsc{Education}}
    \cventry{2012--2015}                                       % year--year
            {Ph.D in Computer Science}                        % degree
            {University of Nantes}                            % institution
            {Nantes}                                          % city
            {France}                                          % country
            {Automatic Domain-Specific Keyphrase Annotation.} % description
    \cventry{2010--2012}
            {Master's degree in Computer Science}
            {University of Nantes}
            {Nantes}
            {France}
            {Software Engineering and Software Architecture.}
    \cventry{2009--2010}
            {Bachelor's degree in Computer Science}
            {University of Nantes}
            {Nantes}
            {France}
            {Software Engineering.}
    \cventry{2007--2009}
            {Associate's degree in Computer Science}
            {Institute of Technology of Nantes}
            {Nantes}
            {France}
            {Software Engineering.}
    \cventry{2004--2007}
            {High school diploma}
            {Joubert High School}
            {Ancenis}
            {France}
            {}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %% Skills and Expertise
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \section{\textsc{Skills}}
    \subsection{Computer Science}
      \cvline{Programming Languages}
             {Ruby, Pyhon, Bash, C, C++, Objective-C, Java, OCaml}
      \cvline{Web Technologies}
             {HTML, PHP, Javascript, Objective-J}
      \cvline{Software Modeling}
             {UML}
      \cvline{Database}
             {Oracle, PostGIS, PL/SQL, JDBC}
      \cvline{Operating System}
             {Mac OS X, Linux, Microsoft Windows}
    \subsection{Language}
      \cvline{French}{Native}
      \cvline{English}{Good}
      \cvline{Japanese}{Beginner}
      \cvline{Vietnamese}{Beginner}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %% Experience
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \section{\textsc{Experience}}
    \cventry{February 2016--Now}
            {Software Engineer}
            {Minimal Technologies}
            {Tokyo}
            {Japan}
            {\textbf{WOVN.io: Website Localization Service}\\
             Backend development (Ruby on Rails); Frontend development (Javascript+Vue.js).}
    \cventry{October 2012--June 2015}           % year--year
            {Teaching Assistant}                % job title
            {Institute of Technology of Nantes} % employer
            {Nantes}                            % city
            {France}                            % country
            {UML, HTML/CSS, and Javascript.}    % desciption
    \cventry{July 2014--October 2014}
            {Internship Student}
            {NII}
            {Tokyo}
            {Japan}
            {\textbf{Automatic Keyphrase Extraction}\\
             Python implementation of a supervised extension of the TopicRank
             keyphrase extraction method.}
    \cventry{March 2012--August 2012}
            {Internship Student}
            {NII}
            {Tokyo}
            {Japan}
            {\textbf{Behavior Imitation on a Humanoid Robot}\\
             C++ system using the Kinect motion tracking device to move the
             humanoid robot NAO.}
    \cventry{July 2011--August 2011}
            {Software Developer}
            {Magic Instinct Software}
            {Nantes}
            {France}
            {\textbf{Web Application for Raster Chart Cropping}\\
             Javascript application to crop maps using the OpenLayers
             framework.}
    \cventry{April 2010--May 2010}
            {Internship Student}
            {Magic Instinct Software}
            {Nantes}
            {France}
            {\textbf{Web Application for Nautical Buoy Tracking}\\
             Objective-J/Cappuccino application to display tracked nautical
             buoys on Google Maps.}
    \cventry{April 2009--June 2009}
            {Internship Student}
            {IRCCyN}
            {Nantes}
            {France}
            {\textbf{Implementation of the OSEK COM External Communication
             Protocol}\\
             C implementation of the OSEK COM external communication protocol
             under the Trampoline real-time operating system.}

  \bibliographystyle{unsrt}
  \bibliography{../publication_en}
  \nocite{*}
\end{document}

